---
title: "industRial practice"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: > 
  Practice applications of anova in design of experiments and gain sensitivity on p value calculation.
---

```{r setup, include=FALSE}
library(tidyverse)
library(scales)
library(learnr)
source("theme_industRial.R")
# ebike_hardening <- industRial::ebike_hardening
ebike_hardening <- read_rds("ebike_hardening.rds")
knitr::opts_chunk$set(echo = FALSE)
```

# Design of Experiments

## Anova

The anova is a well established statistical technique that results from the fine tuning and combination of different statistical methods such as the partitioning of sums of squares, the linear regression and the statistical inference. Sometimes we may take its output as definitive and jump to conclusions like: *the p value is lower than 0.05 so the machine has a problem*. Nevertheless just like most other statistical tools it helps knowing where it comes from and how and when it can be applied.

In the context of design of experiments the anova extends further the t.test lets see how...

## When to apply?

```{r quiz}
quiz(
  question("Which is the primary use of the anova in an industrial DoE (design of experiment)?",
    answer(
      "Compare variances", 
      message = "The name analysis of variance can be considered misleading. In fact the variances (or to be more specific the sums of the squares) are calculated but this is not the primary outcome we're looking for."
      ),
    answer("Compare standard deviations"),
    answer(
      "Compare means",
      "That's it! This approach allows to compare more that two means, thus extending the t.test. It establishes if their difference is statistically different. This provides an indication if the experiment has had an effect.",
      correct = TRUE)
    ,
    answer("Compare ranges"),
    allow_retry = TRUE
  )
)
```

## Data

For the coming exercises we're using the data set ebike_hardening. This data set comes in a *wide* format typically used in day to day data collection situations. For someone in a laboratory or factory shopfloor it is often easier to simple create a new column and add new measurements. Sometimes unfortunately this leads to not very clear headers. Also for ggplots is necessary to specify the factors clearly so a *longer* format makes it easier to deal with in R.

In the following exercise convert the dataset to a narrow format and take the opportunity to calculate the means by group leading to a tibble such as:

```{r echo=FALSE, message=FALSE, warning=FALSE}
ebike_narrow <- ebike_hardening %>%
  pivot_longer(
    cols = starts_with("g"),
    names_to = "observation",
    values_to = "cycles"
  ) %>%
  group_by(temperature) %>%
  mutate(cycles_mean = mean(cycles)) %>%
  ungroup()
head(ebike_narrow)
```


```{r ebike, exercise=TRUE, exercise.lines = 5, exercise.eval=TRUE}

```

```{r ebike-hint}
# start with the ebike_hardening dataset and use the function pivot_longer()
# then group by temperature to calculate the means for each treatment group
```

## The anova sandbox

The anova output can be sometimes tricky to interpret as many things are at play. In the application below we start with a plot similar to the plot of the Anova chapter. It presents boxplots of the distribution of the different treatment groups of the ebike frame hardening process. Outputs correspond to the lifecycle of the frame (in number of cycles to failure) and the groups correspond each to a specific furnace temperature. You can play with the group means, standard deviation and population size.

Try to get to a non significant p value of more than 0.05 by playing with the means (and standard deviations if needed)

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(stats)
library(broom)
filter <- dplyr::filter
select <- dplyr::select

fluidPage(
    titlePanel("The anova sandbox"),
    sidebarLayout(
        sidebarPanel(width = 4,
            sliderInput(inputId = "mean1", "Group 1 target mean:", min = 500000, max = 700000, value = 540000),
            sliderInput(inputId = "mean2", "Group 2 target mean:", min = 500000, max = 700000, value = 575000),
            sliderInput(inputId = "mean3", "Group 3 target mean:", min = 500000, max = 700000, value = 625000),
            sliderInput(inputId = "mean4", "Group 4 target mean:", min = 500000, max = 700000, value = 700000),
            sliderInput(inputId = "sd1", "Group 1 sd:", min = 10000, max = 50000, value = 50000, step = 1000),
            sliderInput(inputId = "sd2", "Group 2 sd:", min = 10000, max = 50000, value = 30000, step = 1000),
            sliderInput(inputId = "sd3", "Group 3 sd:", min = 10000, max = 50000, value = 40000, step = 1000),
            sliderInput(inputId = "sd4", "Group 4 sd:", min = 10000, max = 50000, value = 15000, step = 1000),
            sliderInput(inputId = "n", "Group sample size n:", min = 100, max = 10000, value = 100),
        ),
        mainPanel(width = 8,
           plotOutput("boxplot"),
           DTOutput("analysis")
        )
    )
)
```

```{r context="server"}
    measurements <- reactive({
        tibble(
            group1 = rnorm(mean = input$mean1, sd = input$sd1, n = input$n),
            group2 = rnorm(mean = input$mean2, sd = input$sd2, n = input$n),
            group3 = rnorm(mean = input$mean3, sd = input$sd3, n = input$n),
            group4 = rnorm(mean = input$mean4, sd = input$sd4, n = input$n)) %>% 
        pivot_longer(
            cols = everything(), 
            names_to = "group",
            values_to = "value") %>%
            group_by(group) %>%
            mutate(group_mean = mean(value))
    })
        
    output$boxplot <- renderPlot({

        ggplot(measurements()) +
            geom_boxplot(aes(x = group, y = value, fill = group)) +
            labs(
                title = "Measurements plot",
                subtile = "",
                x = "",
                y = "Value"
            ) +
            scale_fill_viridis_d(option = "D", begin = 0.5) +
            scale_y_continuous(n.breaks = 10, labels = label_number(big.mark = "'")) +
            labs(title = "e-bike frame hardening process",
                 subtitle = "Raw data plot",
                 x = "Furnace Temperature [°C]",
                 y = "Cycles to failure [n]") +
        theme_industRial()
    })
    
    analysis <- reactive({
        aov(value ~ group, measurements()) %>% tidy()
    })
        
    output$analysis <- renderDT({
        analysis() %>%
            datatable(
              options = list(searching = FALSE)
            ) %>%
            formatSignif(columns = 3:4, digits = 1) %>%
            formatRound(columns = 5:6, digits = 2)
    }) 
```

## Anova parameters

Although we tend to take it as a direct calculation when using excel, minitab or another software the anova calculation has many steps to get to the p value and to fully grasp its meaning it is helpful to dig into those aspects.

```{r parameters, echo = FALSE}
question_checkbox(
  "Which parameters influence the anova calculation?",
  answer("the group means", correct = TRUE),
  answer("the group standard deviations", correct = TRUE),
  answer("the sample size", correct = TRUE),
  answer("The absolute value of the output", correct = FALSE, message = "the sample size has no influence if the ratios are the same the p value is the same, e.g. if the lifecycles were all divided by 10"),
  random_answer_order = TRUE,
  allow_retry = TRUE
)
```


inputs and output, distribution of the inputs, the inputs means and variability, the split of the input factors in groups, differences between the means of those factors, the ratio between the groups variabilitiy.
