---
title: "industRial practice"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
dial_control <- read.csv("data/dial_control.csv")
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
# library(industRial)
library(qicharts2)
```

# Design for Six Sigma

## Pareto chart

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

# Pareto chart



```{r}
library(shiny)

# Define UI for application that draws a histogram
# ui <- fluidPage(

    # Application title
    # titlePanel("Old Faithful Geyser Data"),

    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel(
            sliderInput("bins",
                        "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
        ),

        # Show a plot of the generated distribution
        mainPanel(
           plotOutput("distPlot")
        )
    )
# )
```

```{r, context="server"}
# Define server logic required to draw a histogram
# server <- function(input, output) {

    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)

        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
    })
# }

# Run the application 
# shinyApp(ui = ui, server = server)
```


```{r}
fluidPage(
  titlePanel("Dial control pareto charts"),
  sidebarLayout(
    sidebarPanel(
      selectInput(
        inputId = "variable",
        label = "Select variable",
        choices = c("Defect", "Location"),
        selected = "Defect",
        multiple = FALSE
      )
    ),
    mainPanel(
      plotOutput("pareto")
    )
  )
)
```

```{r context="server"}
output$pareto <- renderPlot({
  d_type <-
    dial_control %>% pull(.data[[input$variable]]) %>% as.character()
  paretochart(
    d_type,
    title = "Watch Dial polishing",
    subtitle = "Pareto chart",
    ylab = "Percentage of deffects",
    xlab = "Deffect type",
    caption = "Source: Dial Production Team"
  )
})
```


```{r}
head(dial_control) %>% 
  kable(align = "c", 
        caption = "dial control data", 
        booktabs = T)
```

```{r dial, exercise=TRUE, exercise.eval=TRUE}
d_type <- dial_control %>% pull(Defect) %>% as.character()
paretochart(
  d_type, 
  title = "Watch Dial polishing",
  subtitle = "Pareto chart", 
  ylab = "Percentage of deffects",
  xlab = "Deffect type",
  caption = "Source: Dial Production Team"
  )
```

```{r dial-hint}
head(mtcars)
```
