---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
source(here::here("inst/book/setup.R"))
```

# industRial

<!-- badges: start -->
<!-- badges: end -->

This is the github repository of `{industRial}` the companion package to the book [industRial Data Science](https://j-ramalho.github.io/industRial/index.html).
The goal of this package is to provide data sets and functions to complete the case studies. It also contains all book original files and exercises.

## Installation

<!-- You can install the released version of industRial from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("industRial")
```
-->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("J-Ramalho/industRial")
```

## Example

This is an example from the first case study of the book on a pareto chart that use the data set dial_control and the theme_industrial. 

```{r example}
library(industRial)
library(qicharts2)
d_type <- dial_control %>% pull(Defect) %>% as.character()
paretochart(
  d_type,
  title = "Watch Dial polishing",
  subtitle = "Pareto chart",
  ylab = "Percentage of deffects",
  xlab = "Deffect type",
  caption = "Source: Dial Production Team"
) +
  theme_industRial()
```

Here is another example from the last case study with a custom made process capability chart that use the tablet_weight dataset and the theme_qcc.

```{r}
tablet_weight <- tablet_weight %>%
    janitor::clean_names()
weight_statistics_data <- process_stats(tablet_weight, 9)
chart_Cpk(weight_statistics_data) +
  theme_qcc()
```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example   can be found here: <https://github.com/r-lib/actions/tree/master/examples>.
In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
-->

## Issues

To report any issue or make suggestions please open an issue on the book repository:
[industRialds/issues](https://github.com/J-Ramalho/industRial/issues)
