
```{r}
source(here::here("inst/book/setup.R"))
library(readxl)
```

# R Toolbox

## R Programming

Why R? Many tools exist to do Data Analysis and Statistics with different degrees of power and difficulty such as:

* Spreadsheets: Excel, Libreoffice, Numbers
* Proprietary software: Minitab, Mathlab
* Programming languages: Visual Basic, R, Python, Julia
* Databases: sqlite, postgre, mysql, mongodb

Choosing the right set of tools for Data Science is often not a very scientific task. Mostly is a matter of what is available and what our colleagues, customers or suppliers use. As with everything it is important to remain open to evaluate new tools and approaches and even to be able to combine them.

In this book we've chosen to provide all examples in R which is a free software environment for statistical computing and graphics https://www.r-project.org/
Besides taste and personnal preference R brings a significant number of specific advantages in the field of Industrial Data Science:

1. R allows for reproducible research

This because the algorithms and functions defined to make the calculations can be inspected and all results can be fully reproduced and audited. This is known as reproducible research and is a critical aspect in all areas where a proof is needed such as in equipment validation and product quality reporting.

2. R functions, tools and programs can be adapted and improved

Being an open source language, all R libraries and packages added to the basic environment can be not only audited but adapted and improved This is very important as when we enter into details every industry has a slight different way of doing things, different naming conventions, different coeficients and so on.

3. R is extensible

R is compatible with most other software on the market and is an excellent "glue" tool allowing for example for data loading from excel files, producing reports in pdf and even building complete dashboards in the form of web pages. 

## R Packages and Datasets

All tools applied throughout this book are available in the form of packages of the programming language R. As with all open source code, they're all available for download with freedom to modification and at no cost.

The specific R packages used in the text that come from the data science applications in the industrial world are mentioned in this section. Wherever they are required in the book they are loaded explicitly so that we know where the functions come from.

The generic packages are on the other hand loaded implicitly and not visible in the text. The are typically the `{tidyverse}`, the `{stats}` which we assume the reader is fully acquainted with.

A note on function masking: a common issue in R when compared to python for instance is function masking. As we tend to load all the sets of functions from each package we end up with conflicting function names. In the scope of this text it is mostly the function filter() from `{dplyr}` which conflicts with the function with the same name from `{stats}`. We use the most simple technique which is to add `filter <- dplyr::filter` in the begining of our script to precise which function we want to give priority and we pre-append the package name to all calls of the other function such as `stats::filter`. For more sophisticated ways to handle this issue we suggest the package `{import}`.

### Specific

#### industRial

The `{industRial}` package is an original companion package developed for this book that can be simply downloaded from github with the following command:

```{}
devtools::install_github("J-Ramalho/industRial")
```

The primary package goal is to make easily available all the datasets from all case studies. All dataset presented throughout the book are published either fully anonymized. Once the package is correctly installed it can be loaded in the R session as usual with the library() function:

```{r}
library(industRial)
```

Once loaded the datasets become immediatly available in memory and can directly be used in the examples presented or for further exploration. Lets confirm this invoking the first dataset:

```{r}
dial_control %>%
  head() %>%
  kable()
```

The dateset can be used and manipulated like any other dataset created in the session or loaded otherwise. For example it can be filtered and assigned to a new variable name:

```{r}
dial_peter <- dial_control %>%
  filter(Operator == "Peter") 
dial_peter %>%
  head(2) %>%
  kable()
```

Bseides the datasets the `{industRial}` package also contains toy functions to clean data and plot Statistical Process Control (SPC) charts. The objective here is to showcase how to build such functions and their scope of application is limited to the book case studies. For complete and robust SPC functions we recommend using the `{QCC}` package also described below.

Additionally the package contains theme functions to print and customise the aesthetics of spc charts and other charts. These themes are built on top of the `{ggplot2}` by H.Wickham and `{cowplot}` package by Claus O.Wilke. They aim for an easier modification of the control chart rules and customisation of the plot aesthetics when compared with other more advanced packages for spc such as the qcc. 

The complete list of datasets, themes and functions can be seen by listing all objects from the package. e.g.:

```{r}
ls("package:industRial")
```

or conveniently on the console with industRial:: and then tab. For each function a help page is available and can be obtained the same way as any other R datasets, themes and functions with `?<object>` (e.g. ?chart_xbar)

#### six sigma

SixSigma is a very complete and robust package by Emilio L.Cano [@Cano2015]. It provides well many well tested functions in the area of quality management.

#### qcc

qcc is another extremely complete and solid package. It was developped and is maintained by Luca Scrucca and offers a very large range of statistical process control charts and capability analysis. Short examples in its vignette: [qcc vignette](https://luca-scr.github.io/qcc/articles/qcc.html)

#### qicharts2

I recommend qichart2 specifically for the nice pareto plots. As many niche packages we need to be awere that the number of contributers is small meaning that it cannot be as thouroughly tested as community packages.

#### DoE.base

This package is one of the most complete and vast packages in Design of Experiements. It is a first of a large suite of packages on the topic, it has vast functionality and is extremely well documented.

[DoE.base](http://prof.beuth-hochschule.de/groemping/software/doe/?L=1&print=1)

### car

The Companion for Applied Regression is also used extensively as it contains many usefull functions to assess the performance of linear models and anova. 

### Generic

The amount of packages available is extremely large and growing very fast. When selecting new packages it is recommended to check the latest package update. Packages that have had no improvements since more than a couple of years should be questionned. The field evolves rapidly and compatibility and other issues can become painfull. A way to obtain statistics on package history is on [metacran](https://www.r-pkg.org/) or [RStudio package manager](https://packagemanager.rstudio.com/). 

Below a comprehensive list of the different packages used in the book:

```{r}
installed_packages <- bind_rows(
  installed.packages(lib.loc = .Library) %>% as_tibble(),
  installed.packages(lib.loc = "/home/joao/R/x86_64-pc-linux-gnu-library/4.0/") %>% 
    as_tibble()
)

recommended_packages <- read_excel("data/rpackages.xlsx") %>%
  filter(Used == "y") %>%
  left_join(installed_packages) %>%
  select(Package, Area, Version) %>%
  arrange(Area)

recommended_packages %>%
  kable()
```

### Edition

Many packages are available for editing documention, from notes to blogs up to complete websites. In this book we've opted to use the R package `{Bookdown}` from @Xie2016 further customized with a layout developped by [Matthew J. C. Crump](https://community.rstudio.com/t/bookdown-contest-submission-gitbook-style-tufte-style-for-web-book/11666). 

## R Session

An important aspect to ensure reproducibility of the examples along the time and between users is to have the same programming setup. We're showing below our setup at the time of rendering the book. 

```{r}
devtools::session_info()[[1]]
```

## Disclaimer

This book presents a variety of software tools and recommended approaches for industrial data analysis. It is incumbent upon the user to execute judgement in their use. The author does not provide any guarantee, expressed or implied, with regard to the general or specific applicability of the software, the range of errors that may be associated with it, or the appropriateness of using them in any subsequent calculation, design, or decision process. The author accepts no responsibility for damages, if any, suffered by any reader or user of this handbook as a result of decisions made or actions taken on information contained therein.




